\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{subcaption}
\usepackage{booktabs}

\title{Nonlinear Regression Model}

\begin{document}
\maketitle

\section{Overview}
  This week I worked on implementing the non-linear model we discussed last time. Let $g$ be whatever group we decide to calculate idleness for (Judge or County) and let $i$ be our current observation, which is a judge-county combination. The non-linear model is:

  \begin{align*}
    \mu_g \text{Days}_i &= \beta_P \text{Plea}_i + \beta_T \text{Trial}_i + \epsilon_i
  \end{align*}

  Where we interpret $\mu_g$ to be the utilization of group $g$. I was having a hard time implementing this, so I asked Walter for advice, and he suggested that I define the function $f(\mu_g,\beta_P,\beta_T) = (\mu_g \text{Days}_i - \beta_P \text{Pleas}_i - \beta_T \text{Trials}_i)^2$ and that I use a standard nonlinear optimizer to minimize it. Walter mentioned that I might have convergence problems since the model is not identified (i.e. multiplying all of the coefficients by any constants would still make the equation hold). Given that we want to interpret the $\mu_g$ as utilizations, I decided to add the constraints that $c \leq \mu_g \leq 1$ and that $\beta_T, \beta_P \geq 0$. I also hoped that this would help with identification.

\section{Results}
  The model seems very sensitive to the lower bound, $c$ that we impose. If we let $c=0$, then the optimizer sets all of the coefficients equal to 0. For other values of the lower bound (e.g. 0.6 or 0.7), the $\mu_g$ for most counties/judges ends up being set to the lower bound. I also tried $c=(0.5,0.6,0.65,0.7,0.75)$. I ran this calculating the utilizations for both judges and counties.

  \subsection{County Model}
    The results in this subsection correspond to the model: $\mu_c \text{Days}_i = \beta_P \text{Plea}_i + \beta_T \text{Trial}_i + \epsilon_i$. Where $i$ is a judge-county combination and $c$ is a county. In the table below, the numerical column names correspond to the lower bound used when computing those estimates. For example the column 0.5 contains the estimates of the nonlinear estimation with the constraint that $0.5 \leq \mu_c \leq 1$.

    \begin{table}[H]
      \centering
      % \small
      \caption{County Model}
      \input{../../../output/tables/Exploration/nlreg_County}
    \end{table}

    \subsection{Judge Model}
      The results in this subsection correspond to the model: $\mu_j \text{Days}_i = \beta_P \text{Plea}_i + \beta_T \text{Trial}_i + \epsilon_i$. Where $i$ is a judge-county combination and $j$ is a judge. In the table below, the numerical column names correspond to the lower bound used when computing those estimates. For example the column 0.5 contains the estimates of the nonlinear estimation with the constraint that $0.5 \leq \mu_j \leq 1$.

      \begin{table}[H]
        \centering
        \small
        \caption{Judge Model}
        \input{../../../output/tables/Exploration/nlreg_JudgeID}
      \end{table}


\end{document}
