\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

\title{May 27, 2021 Meeting Agenda}

\begin{document}
\maketitle

\section{Joint estimation of $\mu_p$ and $\mu_t$}
I was mostly able to implement step 4 of the ad-hoc algorithm. This is the step where for a given $\theta$ and number of plea days, $N$, we find the $\mu_p$ that minimizes the negative log likelihood (NLL). I'm using a gradient descent algorithm, so the immediate next step is to figure out a good stopping criterion for the gradient descent algorithm. I was planning on stopping once there has been no improvement after 5 iterations. For context, this is what we minimize in step 4:
\begin{align*}
  \min L(\mu_p) &= -\sum_{i=1}^N \log P(S_i = s)\\
  P(S_i = s) &= \frac{\theta^s e^{-\theta}}{s!}[1-\sum_{k=1}^{s-1}\frac{\mu_p^k e^{-\mu_p}}{k!}] + \frac{\mu_p^s e^{-\mu_p}}{s!}[1-\sum_{k=1}^s \frac{\theta^k e^{-\theta}}{k!}]
\end{align*}
  \subsection{Problems}
    \begin{itemize}
      \item Our current best guess of $\mu_p$ is 10.7. However, as part of our probability calculation, we have to compute $\mu_p^s$, where $s$ is the number of pleas a judge heard in a day. Trying to compute $\mu_p^s$ for values of $s$ greater than 20 raises an error. I think this is because the largest integer value allowed by the deep learning package I'm using for the gradient calculation is a little less than $10^{18}$. I'm currently only using values of $s \leq 15$.
      \item Step 4 is currently a bit slow, it takes 1 or 2 minutes to find the value of $\mu_p$ that minimizes the NLL for a given value of $\theta$.
    \end{itemize}

  \subsection{Next Steps}
  \begin{itemize}
    \item Figure out a stopping criteria for gradient descent algorithm.
    \item Figure out what to do about days with more than 20 pleas. For context, 14, 16, and 17 are the 96th, 97th, and 98th percentile for pleas sentenced in a day in tha dataset.
    \item Finish implementing full algorithm (i.e. include updating of $\mu_t$, $\theta$, and $N$)
    \item Implement exclusion criteria for clean days.
  \end{itemize}

\end{document}
